Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-22 src/tex/appendicies.tex
add more plots with more stable looking results

We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
their respective hyper-parameters and prior distributions in the next section. To calculate marginal likelihoods and draw 
samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}. We also make use of the hamiltonian monte carlo algorithms in 
\textsc{numpyro} and use \textsc{jax} to calculate our likelihoods \bruce{FIND citations for these}.

\section{Models and Hyper-Parameters} \label{sec:hypparams}

@@

>>>>

We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
their respective hyper-parameters and prior distributions in the next section. To calculate draw 
samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
NUTS hamiltonian monte carlo sampler in \textsc{numpyro} and \textsc{jax} to calculate likelihoods \bruce{FIND citations for these}.

@@

\section{Penalized Splines and Smoothing}\label{sec:psplines}

A common issue when using splines as a flexible fitting method is their sensitivity to the chosen number of knots, and their locations. 
Adding more knots knots will increase the natural a-priori variance in the spline function, while the space between knots can limit the 
resolution of features in the data the spline is capable of fitting. To ensure your spline based model is flexible enough to find sharp
features in data, one would want to add as many knots as densely as possible, but this comes with the sometimes un-wanted affect of the 
larger variance as mentioned above. To overcome this we resort to the frequentist penalized spline (PSpline) in which one applies a penalty
to the likelihood based on the difference of adjacent knot coeficients. Since the resulting linear combination of spline basis components is 
smoother, or flatter, when the basis coeficients are near each other, this has a natural smoothing affect to the spline function. Since we are 
using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog, by applying 
the stochastic differnece prior described in \bruce{CITE THIS PAPER}, which is equivalent to a Gaussian random walk prior where each succeeding 
coeficient is normally distributed about its neighboring coeficients. Thus the smoothing prior for $n$ degree's of freedom basis with a smoothing 
difference order of $r$ is defined as:

\begin{eqnarray}
\tau_\lambda \sim \mathcal{G}(a, b), \\
p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
\end{eqnarray}

\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution, such that
the mean is at 1, with a large vairabce. This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. 
By adding in a very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
the data can be described smoothly, and relax when the data has features for the spline function to fit. In practice one would want to add knots 
of order the number of observations or more. One downside of this prior specification is a moderate dependence on choice of the b hyper-parameter for 
Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method in \bruce{CITE BAYESIAN PSPLINES} where we construct 
a mixture model on a wide range of gamma distributions with different b hyper-parameters. We can now replace the prior on $\tau_\lambda$ with:

\begin{align}
    \bm{p} \sim \mathcal{D}(m), \\
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
\end{align}

Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:

\begin{eqnarray}
\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
\end{eqnarray}

Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
the power-law like mass distributions that are commonly used.

Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
we must ensure that the spline function is in fact flat or smooth with all equal coeficients. We follow the distinction from \bruce{CITE bayesian psplines} that the difference
penalty or prior is only valid with ``proper'' spline bases. This is where the knots are evenly spaced and are not stacked at the extremal values, 
as is sometimes done. Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. The ``proper''
basis is shown on the left where the resulting (black) curve is flat with equal components, while the ``improper'' basis on the right has the 
components squeezed up against the boundaries where multiple knots are located causing the sharp increases at the bounds even with all 10 coeficients equal.
*\

### 2022-09-22 src/tex/methods.tex
add more plots with more stable looking results

\section{Methods} \label{sec:methods}

\subsection{Constructing A Basis} \label{sec:basis_splines}

@@

\begin{equation}
    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t}) + \\
                                \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
\end{equation}

@@

@@

\subsection{Penalized Splines}
A common issue when using splines as a flexible fitting method is their sensitivity to the chosen number of knots, and their locations. 
Adding more knots knots will increase the natural a-priori variance in the spline function, while the space between knots can limit the 
resolution of features in the data the spline is capable of fitting. To ensure your spline based model is flexible enough to find sharp
features in data, one would want to add as many knots as densely as possible, but this comes with the sometimes un-wanted affect of the 
larger variance as mentioned above. To overcome this we resort to the frequentist penalized spline (PSpline) in which one applies a penalty
to the likelihood based on the difference of adjacent knot coeficients. Since the resulting linear combination of spline basis components is 
smoother, or flatter, when the basis coeficients are near each other, this has a natural smoothing affect to the spline function. Since we are 
using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog, by applying 
the stochastic differnece prior described in \bruce{CITE THIS PAPER}, which is equivalent to a Gaussian random walk prior where each succeeding 
coeficient is normally distributed about its neighboring coeficients. Thus the smoothing prior for $n$ degree's of freedom basis with a smoothing 
difference order of $r$ is defined as:

\begin{eqnarray}
\tau_\lambda \sim \mathcal{G}(a, b), \\
p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}}
\end{eqnarray}

\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution, such that
the mean is at 1, with a large vairabce. This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. 
By adding in a very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
the data can be described smoothly, and relax when the data has features for the spline function to fit. In practice one would want to add knots 
of order the number of observations or more. One downside of this prior specification is a moderate dependence on choice of the b hyper-parameter for 
Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method in \bruce{CITE BAYESIAN PSPLINES} where we construct 
a mixture model on a wide range of gamma distributions with different b hyper-parameters. We can now replace the prior on $\tau_\lambda$ with:

\begin{eqnarray}
\bm{p} \sim \mathcal{D}(m), \\
p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
\end{eqnarray}

Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:

\begin{eqnarray}
\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c}}
\end{eqnarray}

Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
the power-law like mass distributions that are commonly used.

\begin{figure*}[ht!]
    \script{spline_basis_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing proper (left) and improper (right) MSpline bases with 20 degrees of freedom and equal weights for each component. The 
            difference penalty as described in Section II hinges on the fact that basis coeficients that are close produce smoother or flatter 
            curves. This means one does not want to use an improper basis (i.e. right) with a difference penalty as the resulting curve is not flat 
            with each component having equal weights.}
        \label{fig:spline_basis}
    \end{centering}
\end{figure*}

Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
we must ensure that the spline function is in fact flat or smooth with all equal coeficients. We follow the distinction from \bruce{CITE bayesian psplines} that the difference
penalty or prior is only valid with ``proper'' spline bases. This is where the knots are evenly spaced and are not stacked at the extremal values, 
as is sometimes done. Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. The ``proper''
basis is shown on the left where the resulting (black) curve is flat with equal components, while the ``improper'' basis on the right has the 
components squeezed up against the boundaries where multiple knots are located causing the sharp increases at the bounds even with all 10 coeficients equal.

\subsection{Model Specfication}

We use hierarchical Bayesian inference to simultaneosly infer the mass, spin and redshift distributions of binary black holes (BBHs) using 
the 69 confident BBH detections reported in the recent LVK catalog of observations, GWTC-3. In particular we choose to parameterize the two
masses with the primary (more massive component) mass and the mass ratio defined as $q=\frac{m_2}{m_1}$. We choose to model 4 of the 6 total 
spin degrees of freedom of a binary merger with each component spin magnitude, and the cosine of the tilt angle which is defined as the angle 
between each spin vector and the binaries orbital angular mommentum vector. We additionally will fit a population model on the redshift distribution
of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology defined by the Planck 2015 results, which defines an analytical mapping between each event's inferred
luminosity distance and it's redshift. While we choose to use MSpline distibutions for the masses and spins, we use the canonical \textsc{PowrerlawRedshift}
model describing the evolution of CBC merger rates as a power law in $(1+z)$ with a slope of $\lambda_z$. The corresponsing distribution is Thus
desribed by $p(z|\lambda)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda$. We model the spin magnitude and tilt distibutions to be 
described by independent MSpline distributions for each component.

>>>>

\section{Constructing A Basis} \label{sec:basis_splines}

@@

\begin{multline*}
    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t})\\
                                + \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
\end{multline*}

@@

\begin{figure}[ht!]
    \script{spline_basis_plot.py}
        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing proper MSpline bases with 20 degrees of freedom and equal weights for each component.}
        \label{fig:spline_basis}
\end{figure}

@@

\section{Model Construction}

\bruce{placeholder paragraph here to introduce our model constructions.}
We use hierarchical Bayesian inference to simultaneosly infer the mass, spin and redshift distributions of binary black holes (BBHs) using 
the 69 confident BBH detections reported in the recent LVK catalog of observations, GWTC-3. In particular we choose to parameterize the two
masses with the primary (more massive component) mass and the mass ratio defined as $q=\frac{m_2}{m_1}$. We choose to model 4 of the 6 total 
spin degrees of freedom of a binary merger with each component spin magnitude, and the cosine of the tilt angle which is defined as the angle 
between each spin vector and the binaries orbital angular mommentum vector. We additionally will fit a population model on the redshift distribution
of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology defined by the Planck 2015 results, which defines an analytical mapping between each event's inferred
luminosity distance and it's redshift. While we choose to use MSpline distibutions for the masses and spins, we use the canonical \textsc{PowrerlawRedshift}
model describing the evolution of CBC merger rates as a power law in $(1+z)$ with a slope of $\lambda_z$. The corresponsing distribution is Thus
desribed by $p(z|\lambda)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda$. We model the spin magnitude and tilt distibutions to be 
described by independent MSpline distributions for each component.

### 2022-09-22 src/tex/ms.tex
add more plots with more stable looking results

\title{Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Popuation Properties}

@@

\section{Acknowledgements}\label{sec:acknowledments}
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{bilby}~\citep{Ashton_2019},
\textsc{GWPopulation}~\citep{Talbot_2019},
\textsc{jax},
\textsc{numpyro},
\textsc{arviz},
\textsc{seaborn},
\textsc{corner} \bruce{CITE ALL ABOVE}
}
\bibliography{bib}{}
\bibliographystyle{aasjournal}

>>>>

\title{Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population}

@@

\section{Acknowledgements}\label{sec:acknowledments}
We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful and discussions during the preparation this manuscript, 
along with helpful comments on an early draft by Tom Callister.
This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
fully funded by the National Science Foundation.
\software{
\textsc{Astropy}~\citep{2018AJ....156..123A},
\textsc{NumPy}~\citep{harris2020array},
\textsc{Matplotlib}~\citep{Hunter:2007},
\textsc{jax},
\textsc{numpyro},
\bruce{CITE ALL ABOVE}
}
\bibliography{bib}{}
\bibliographystyle{aasjournal}

### 2022-09-22 src/tex/results.tex
add more plots with more stable looking results

\section{Population Inference of GWTC-3 BBHs} \label{sec:results}

\subsection{Mass Distribution} \label{sec:mass_dist}

@@

\begin{figure*}[ht!]
    \script{mass_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
        \caption{Plot showing the primary mass (left) and mass ratio (right) distributions inferred with the 
        \textsc{MSpline} model (black) with 40 knots for $m_1$, and 15 knots for $q$. We show the results for the \textsc{PowerlawPeak} (blue) and 
        \textsc{PowerlawSpline} (orange) models fromthe LVK's GWTC-3 population analyses. Solid lines show the median of the posterior while the shaded
        bands show the 90\% credible intervals.}
        \label{fig:mass_distribution}
    \end{centering}
\end{figure*}

@@

\subsection{Spin Distributions} \label{sec:spin_dist}

The spins distribution of merging combact binaries provides a very useful insight into the formation history of the binary. In particular the two main subcategories, 
the isolated and dynamical formation channels, would produce distinct signatures in the spin distribution when looking at a population of observations. Isolated formation
is where the only interactions with the binary are between each other. As the binary evolves and mass transfer happens between the two components, we expect the orientation
of each components spin vector to be preferentially aligned with the orbital angular mommentumof the system. Some misalignment is epected to occur due to the kicks from 
each star exploding in supernovae leaving behind the compact objects. Conversely, the dynamical channel

\begin{figure*}[ht!]
    \script{component_spin_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
        \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
        \label{fig:component_spin_distribution}
    \end{centering}
\end{figure*}

\begin{figure*}
    \script{iid_component_spin_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/iid_component_spin_distribution_plot.pdf}
        \caption{Plot showing the inferred component spin magnitude (left) and spin tilt (right) distributions inferred with the 9-knot \textsc{MSpline} models. 
        Each components spin magnitude and tilt are assumed to be IID. We compare by showing the results for the
        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
        \label{fig:iid_component_spin_distribution}
    \end{centering}
\end{figure*}

>>>>

\section{Binary Black Hole Population Inference with GWTC-3} \label{sec:results}

\bruce{intro paragraph here to describe GWTC3 catalog and the selection we made for our analyses}

\subsection{BBH Mass Distibution} \label{sec:mass_dist}

@@

\begin{figure*}[ht!]
    \script{mass_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
        \caption{Plot showing the primary mass distribution inferred with the \textsc{MSpline} model with 40 knots for $m_1$. We show the results for the 
        \textsc{PowerlawSpline} (blue) model from the LVK's GWTC-3 population analyses.}
        \label{fig:mass_distribution}
    \end{centering}
\end{figure*}

@@

\subsection{BBH Component Spin Distributions} \label{sec:spin_dist}

The spins distribution of merging combact binaries provides a very useful insight into the formation history of the binary. In particular the two main subcategories, 
the isolated and dynamical formation channels, would produce distinct signatures in the spin distribution when looking at a population of observations. Isolated formation
is where the only interactions with the binary are between each other. As the binary evolves and mass transfer happens between the two components, we expect the orientation
of each components spin vector to be preferentially aligned with the orbital angular mommentumof the system. Some misalignment is epected to occur due to the kicks from 
each star exploding in supernovae leaving behind the compact objects. Conversely, the dynamical channel     
\begin{figure}
    \script{plot_iid_spinmag.py}
    \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
    \caption{Caption.}
    \label{fig:iid_spinmag_dist}
\end{figure}

\begin{figure}
    \script{plot_iid_spintilt.py}
    \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
    \caption{Caption.}
    \label{fig:iid_spintilt_dist}
\end{figure}
%\begin{figure*}[ht!]
%    \script{component_spin_distribution_plot.py}
%    \begin{centering}
%%        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
 %       \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
%        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
%        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
%        \label{fig:component_spin_distribution}
%    \end{centering}
%\end{figure*}

%\begin{figure*}
%    \script{iid_component_spin_distribution_plot.py}
%    \begin{centering}
%        \includegraphics[width=\textwidth]{figures/iid_component_spin_distribution_plot.pdf}
%        \caption{Plot showing the inferred component spin magnitude (left) and spin tilt (right) distributions inferred with the 9-knot \textsc{MSpline} models. 
%        Each components spin magnitude and tilt are assumed to be IID. We compare by showing the results for the
%        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
%        \label{fig:iid_component_spin_distribution}
%    \end{centering}
%\end{figure*}

Comment here are the inferences of iid model vs Default and then iid vs independent test pointing out possible reasons for why spin tilt 
does not peak at cos theta = 1 i.e. salvo's paper

\subsection{The Effective Spin Dimensions}

Transform comp spin results to effective dims to see how strong changes in mag/tilt dont significantly affect our best constrained/measured
effective spins

Present results fitting chi eff dist with MSpline I am making a change.

\subsection{Discussion}

\begin{figure}
    \script{plot_ind_spinmag.py}
    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
    \caption{Caption.}
    \label{fig:ind_spinmag_dist}
\end{figure}

\begin{figure}
    \script{plot_ind_spintilt.py}
        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
        \caption{Caption.}
        \label{fig:ind_spintilt_dist}
\end{figure}

\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}
